Environmental behaviour & practices

### 2021-01-19 03-comportements.Rmd
adding the minmapping for all
figure mermaid corrections

---
```{r, include=FALSE}
require(DiagrammeR)
require(tidyverse)
require(kableExtra)
```

@@

@@

mermaid("
graph LR
  A[\"Attitude toward the act (Att)\"]-->D[Behavioural Intention]
  B[\"Subjective Norm (SN)\"]-->D[Behavioural Intention]
  C[\"Perceived Behavioural Control (PBC)\"]-->D[Behavioural Intention]
  D[Behavioural Intention]-->E[Behaviour]
  C[Perceived Behavioural Control]-.->E[Behaviour]

  classDef className font-size:20px;
  class A,B,C,D className;
")
```

@@

>>>>

---
```{r, include=FALSE}
require(DiagrammeR)
require(tidyverse)
require(kableExtra)
require(widgetframe)
```

@@

:::l-page
<div style="width: 100%; height: 480px; margin: auto; position: relative; text-align: center;"><iframe allowfullscreen frameborder="0" style="width:99%; height:480px" src="https://lucid.app/documents/embeddedchart/945c1be7-a621-4c3e-9267-f77f2fb2855a" id="CJG60F2Mr.Uj"></iframe></div>
:::

@@

mermaid("
graph LR
  A[Attitude toward the act <br/> -ATT-]-->D[Behavioural Intention <br/>]
  B[Subjective Norm -SN-<br/>]-->D[Behavioural Intention]
  C[Perceived Behavioural Control -PBC-<br/>]-->D[Behavioural Intention]
  D[Behavioural Intention <br/>]-->E[Behaviour]
  C[Perceived Behavioural Control -PCB-]-.->E[Behaviour]

  classDef className font-size:18px, height:60px ;
  class A,B,C,D className;
")

#
#  
```

@@

```{r, include=TRUE, layout="l-page", echo=FALSE}
